---
title: "Linear Model with Prediction"
author: "Denise Sahagun"
date: "5/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)
```

## R Markdown

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 

You can import the data directly from a link to its website.  Copy that link to the clipboard by right clicking on Raw Data and then copy link.

Then issue

data <- read.csv(file="paste link here",sep="",header=TRUE)  

that sep=""  in the command is needed since the file is space delimited, not comma separated.  The header=TRUE is also necessary so that the names of the variables and their formats get correctly imported.

New aspects of this assignment

You need to create your Rmarkdown file without a starting template
You need to create a new github repo from scratch

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)
```

```{r}
plot(SIMS~ARM,data=data)
```

##Now with ggplot - first select the basic data

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

##Now add in scatterplot

```{r}
basicNN + geom_point()
```

# now add the model fit to our plot

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 
# Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

# Inferential  (Build linear model)
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

This is the equation of Blue Lime SIMS= -4.10 + ARM 0.055


## Prediction

```{r}
newdata <- data.frame(ARM = 88, GRIP = 94)
predict (model.1, newdata = newdata, interval = "prediction")
```
# SIMS~GRIP

### Scatterplot
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 

### Numerical results

```{r}
cor(SIMS~GRIP,data=data)
```

# Inferential  (Build linear model)
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.1)
```

## Prediction

```{r}
newdata <- data.frame(GRIP = 88, ARM = 94)
predict (model.1, newdata = newdata, interval = "prediction")
```

Residual standard error is 1.295 and adjusted R squared is 4.053

# SIMS~ARM+GRIP

### Numerical results

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

# Inferential  (Build linear model)
  
```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.1)
```

## Prediction

```{r}
new <- data.frame(ARM = 88, GRIP = 94)
```

```{r}
predict(model.3, new, interval = "prediction", level = .95)
```

This line shows that SIMS is equal to -5.4  + 0.47 * ARM  + 0.82 * GRIP. The R squared is 0.536 and the residual standard error is 1.144

